### 2022-01-02 acm-template/article.tex
gitignore and ACM template

%%
%% This is file `sample-manuscript.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `manuscript')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-manuscript.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
%%%% Small single column format, used for CIE, CSUR, DTRAP, JACM, JDIQ, JEA, JERIC, JETC, PACMCGIT, TAAS, TACCESS, TACO, TALG, TALLIP (formerly TALIP), TCPS, TDSCI, TEAC, TECS, TELO, THRI, TIIS, TIOT, TISSEC, TIST, TKDD, TMIS, TOCE, TOCHI, TOCL, TOCS, TOCT, TODAES, TODS, TOIS, TOIT, TOMACS, TOMM (formerly TOMCCAP), TOMPECS, TOMS, TOPC, TOPLAS, TOPS, TOS, TOSEM, TOSN, TQC, TRETS, TSAS, TSC, TSLP, TWEB.
% \documentclass[acmsmall]{acmart}

%%%% Large single column format, used for IMWUT, JOCCH, PACMPL, POMACS, TAP, PACMHCI
% \documentclass[acmlarge,screen]{acmart}

%%%% Large double column format, used for TOG
% \documentclass[acmtog, authorversion]{acmart}

%%%% Generic manuscript mode, required for submission
%%%% and peer review
\documentclass[manuscript,screen,review]{acmart}
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%
%  Uncomment \acmBooktitle if th title of the proceedings is different
%  from ``Proceedings of ...''!
%
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
 June 03--05, 2018, Woodstock, NY} 
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \country{USA}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf,authordraft]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-authordraft.tex'.

### 2022-01-04 article/article.tex
added author, CSS, keywords and reduced bib

--- 2022-01-02 acm-template/article.tex
@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{XXXXXXX.XXXXXXX}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2018}{Woodstock, NY}
-%
-%  Uncomment \acmBooktitle if th title of the proceedings is different
-%  from ``Proceedings of ...''!
-%
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
- June 03--05, 2018, Woodstock, NY} 
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+\copyrightyear{2022}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title is Hope}
+\title{Literature review of Formal Methods applied to Blockchain technology}
 
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+
+\author{Henoch Vitureira}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \country{USA}
-  \postcode{43017-6221}
-}
-
-\author{Lars Th{\o}rv{\"a}ld}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \country{USA}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{%
-  \institution{The Kumquat Consortium}
-  \city{New York}
-  \country{USA}}
-\email{jpkumquat@consortium.net}
+  \institution{Instituto Politécnico de Setúbal}
+  \city{Setúbal}
+  \country{Portugal}}
+\email{2016041081}
 
@@
      <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+         <concept_id>10011007.10011074.10011099.10011105</concept_id>
+         <concept_desc>Software and its engineering~Process validation</concept_desc>
          <concept_significance>500</concept_significance>
@@
      <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+         <concept_id>10002978.10002979</concept_id>
+         <concept_desc>Security and privacy~Cryptography</concept_desc>
+         <concept_significance>500</concept_significance>
          </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Software and its engineering~Process validation}
+\ccsdesc[500]{Security and privacy~Cryptography}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{Software Quality, Formal Methods, Blockchain, Smartcontracts}
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{base-bib}
 

### 2022-01-05 article/article.tex
cover building

@@
 %%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
 %% end of the preamble, start of the body of the document source.
@@
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
 \title{Literature review of Formal Methods applied to Blockchain technology}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
 
@@
   \institution{Instituto Politécnico de Setúbal}
+  \streetaddress{Campus do IPS - Estefanilha, 2910-761}
   \city{Setúbal}
   \country{Portugal}}
-\email{2016041081}
+\email{2016041081@estudantes.ips.pt}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\renewcommand{\shortauthors}{Henoch Vitureira}
 
@@
 
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
-  \includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base
-  seats. Ichiro Suzuki preparing to bat.}
-  \label{fig:teaser}
-\end{teaserfigure}
-
 %%
@@
 author's own version, with {\itshape very} few changes to the source.
-
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Template Styles}
-
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
-
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigconf,authordraft]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
 
@@
 
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
+  Some examples.  A paginated journal article \cite{Afzaal2021}, an
+  enumerated journal article \cite{Murray2019}, a reference to an entire
+  issue \cite{Matsuo2017}, a monograph (whole book) \cite{Duan2018}, a
   monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
+  \cite{Kawahara2020}, a divisible-book such as an anthology or compilation
+  \cite{Liu2019} followed by the same example, however we only output
+  the series if the volume number is given.
 

### 2022-01-06 article/article.tex
simplified template

--- 2022-01-04 article/article.tex
@@
 %%
-%% This is file `sample-manuscript.tex',
-%% generated with the docstrip utility.
+%% This is file `article.tex',
 %%
-%% The original source files were:
+%% Commands for TeXCount
+%TC:macro \cite [option:text,text]
+%TC:macro \citep [option:text,text]
+%TC:macro \citet [option:text,text]
+%TC:envir table 0 1
+%TC:envir table* 0 1
+%TC:envir tabular [ignore] word
+%TC:envir displaymath 0 word
+%TC:envir math 0 word
+%TC:envir comment 0 0
 %%
-%% samples.dtx  (with options: `manuscript')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-manuscript.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
 %%
 %% The first command in your LaTeX source must be the \documentclass command.
-%%%% Small single column format, used for CIE, CSUR, DTRAP, JACM, JDIQ, JEA, JERIC, JETC, PACMCGIT, TAAS, TACCESS, TACO, TALG, TALLIP (formerly TALIP), TCPS, TDSCI, TEAC, TECS, TELO, THRI, TIIS, TIOT, TISSEC, TIST, TKDD, TMIS, TOCE, TOCHI, TOCL, TOCS, TOCT, TODAES, TODS, TOIS, TOIT, TOMACS, TOMM (formerly TOMCCAP), TOMPECS, TOMS, TOPC, TOPLAS, TOPS, TOS, TOSEM, TOSN, TQC, TRETS, TSAS, TSC, TSLP, TWEB.
-% \documentclass[acmsmall]{acmart}
+\documentclass[sigconf, nonacm]{acmart}
 
-%%%% Large single column format, used for IMWUT, JOCCH, PACMPL, POMACS, TAP, PACMHCI
-% \documentclass[acmlarge,screen]{acmart}
-
-%%%% Large double column format, used for TOG
-% \documentclass[acmtog, authorversion]{acmart}
-
-%%%% Generic manuscript mode, required for submission
-%%%% and peer review
-\documentclass[manuscript,screen,review]{acmart}
-%% Fonts used in the template cannot be substituted; margin 
-%% adjustments are not allowed.
 %%
@@
 %% complete the rights form.
-\copyrightyear{2022}
+\setcopyright{rightsretained}
+\copyrightyear{2021}
+%\settopmatter{printccs=true, printacmref=true}
 
@@
 \affiliation{%
-  \institution{Instituto Politécnico de Setúbal}
+  \institution{Polytechnic Institute of Setubal}
+  \streetaddress{Campus do IPS - Estefanilha, 2910-761}
   \city{Setúbal}
   \country{Portugal}}
-\email{2016041081}
+\email{2016041081@estudantes.ips.pt}
 
@@
 \begin{verbatim}
-\documentclass[sigconf,authordraft]{acmart}
+\documentclass[sigconf]{acmart}
 \end{verbatim}
@@
     \toprule
-    Non-English or Math&Frequency&Comments\\
+    Non-English or Math & Frequency   & Comments          \\
     \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+    \O                  & 1 in 1,000  & For Swedish names \\
+    $\pi$               & 1 in 5      & Common in math    \\
+    \$                  & 4 in 5      & Used in business  \\
+    $\Psi^2_1$          & 1 in 40,000 & Unexplained usage \\
     \bottomrule
@@
     \toprule
-    Command &A Number & Comments\\
+    Command                    & A Number & Comments         \\
     \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
+    \texttt{{\char'134}author} & 100      & Author           \\
+    \texttt{{\char'134}table}  & 300      & For tables       \\
+    \texttt{{\char'134}table*} & 400      & For wider tables \\
     \bottomrule
@@
 
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
+Some examples.  A paginated journal article \cite{Afzaal2021}, an
+enumerated journal article \cite{Murray2019}, a reference to an entire
+issue \cite{Matsuo2017}, a monograph (whole book) \cite{Duan2018}, a
 monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
+\cite{Kawahara2020}, a divisible-book such as an anthology or compilation
+\cite{Liu2019} followed by the same example, however we only output
+the series if the volume number is given.
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{base-bib}
+\bibliography{article-base}
 
@@
 %%
-%% End of file `sample-authordraft.tex'.
+%% End of file `article.tex'.

### 2022-01-09 article/article.tex
add software quality book ref, modelling section

@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
+  Vestibulum enim nibh, aliquet sit amet ex suscipit, efficitur fringilla enim. 
+  Vestibulum elementum fringilla sodales. Cras malesuada sollicitudin consectetur.
+  Cras elit nibh, tempus elementum dui vitae, sagittis porttitor elit. In sollicitudin purus neque, eu tristique felis varius in. Morbi sed commodo eros.
+  Pellentesque ornare sed felis et bibendum.
 \end{abstract}
@@
 
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
-  \includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base
-    seats. Ichiro Suzuki preparing to bat.}
-  \label{fig:teaser}
-\end{teaserfigure}
-
 %%
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
+The rising complexity of features offered by software gives us the ability to use it for the most integrity and reliability dependent needs of our lives. 
+Information systems that rely on these base principles can be financial and health related services, and in most recent times, blockchain based applications. 
+Blockchain, being a decentralized and distributed network protocol that can be used as the core of a monetary system that performs peer-to-peer transactions, 
+it needs the assurance of coordination and consensus of its economy’s state~\cite{Duan2018}. 
+Knowing that the protocol of a given blockchain project is what dictates how transactions and their coordination is maintained, the assurance of security and safety is a given. 
+Formal methods can be introduced in order to provide unequivocal evidence that a given blockchain system and its consensus algorithm are secure and in according to expected software quality.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+Formal methods are a rigorous description of a system or process using mathematics that aims to provide evidence of its reliability and robustness, 
+according the specification in question~\cite{Regan2014}.
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+//TODO FINISH
+
+\section{Formal Modeling Application}
+Blockchain systems can be divided into five main layers~\cite{Duan2018}: Blockchain system, Consensus, Smartcontract and Application. 
+As seen on Figure~\ref{fig:blockchain-layers}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{blockchain-layers}
+  \caption{Blockchain infrastructure, from \cite{Duan2018}}
+  \Description{Ilustration of the layers that describe a blockchain system}
+  \label{fig:blockchain-layers}
+\end{figure}
 
@@
 
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-  \item {\verb|sidebar|}:  Place formatted text in the margin.
-  \item {\verb|marginfigure|}: Place a figure in the margin.
-  \item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
-
-%%
-%% The acknowledgments section is defined using the "acks" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acks}
-  To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
-
 %%

### 2022-01-11 article/article.tex
finish formal application

@@
 
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
+\usepackage{listings}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Software Quality, Formal Methods, Blockchain, Smartcontracts}
+\keywords{Software Quality, Formal Methods, Blockchain, Smart contracts}
 
@@
 \section{Formal Modeling Application}
-Blockchain systems can be divided into five main layers~\cite{Duan2018}: Blockchain system, Consensus, Smartcontract and Application. 
+Blockchain systems can be divided into five main layers~\cite{Duan2018}: Data layer, Consensus layer, Smart contract layer and Application layer. 
 As seen on Figure~\ref{fig:blockchain-layers}.
@@
   \end{figure}
+
+The data layer is responsible for block generation, the construction of the blockchain and storage~\cite{Duan2018}. 
+The network layer connects the data and filters packets, and also manages the nodes. 
+The rules of how the blockchain protocol must work are defined on the consensus layer. 
+This includes agreement between nodes, fault tolerance and data consistency. 
+Smart contracts have their execution lifecycle on the smart contact layer.
+The application layer is the upper level layer of used applications such as games or decentralized financial services.
+
+It is possible to use languages to define the standards of a blockchain system with mathematical rigor.
+One of them is SDL (Specification and Description Language), an Object-Oriented formal language defined by the International Telecommunications Unit.
+It is capable of mathematically describing the structure, behavior, and data of real-time and distributed communicating systems. 
+It is also used by IEEE for standard definition~\cite{Duan2018}.
+
+With SDL, we can describe a structure at the levels of system, block or process. A system represents the object to describe. 
+It is responsible for the communication with the outer environment through the appropriate channels.
+A system can contain one or more blocks and blocks contain one or more processes.
+The majority of the functionality of an SDL system is described on the process level.
+Comparing to conventional programming languages, modules are represented by blocks in SDL, and funcionalities are represented by processes.
+In~\cite{Duan2018}, the authors propose a hierarchical model focused on the consensus layer.
+
+  \subsection{Data Structure}
+  In~\cite{Duan2018} the modelled blockchain system used an Improved Byzantine Fault Tolerant Algorithm as the consensus algorithm.
+  To define the data structure of a block in SDL, we need to represent them as a pair with a header BT and body BH, where:
+
+  \begin{displaymath}
+    B~\equiv(B_H,B_T) \quad \textrm{with} \quad B_H~\equiv(\mathbb{H}_p,\mathbb{H}_a,\mathbb{H}_t,\mathbb{H}_m,\mathbb{H}_h) 
+  \end{displaymath}
+  \begin{displaymath}
+    \quad \textrm{and} \quad B_T~\equiv(T_1,T_2,...,T_{\mathbb{H}_l}) 
+  \end{displaymath}
+  \linebreak[1]
+
+  In these expressions, $\mathbb{H}_p$ represents the hash value of the previous block, 
+  $\mathbb{H}_p$ the hash value of the current block, $\mathbb{H}_t$ it's timestamp, 
+  $\mathbb{H}_m$ the merkle tree root (the hash of the transactions of a block), and $\mathbb{H}_h$ the current block's height.
+
+  The the block' structure definition can be seen on Listing~\ref{lst:block-code}.
+
+  \begin{lstlisting}[frame=single,label={lst:block-code},
+    caption={Definition of a block's structure},captionpos=b]
+    newtype blockchain struct
+      prehash integer;
+      hash integer;
+      length integer;/*the length of blocks*/
+      merkleroot integer;
+      ti Time;/*Timestamp*/
+      translist list;
+    endnewtype;
+
+    newtype list
+     array(maxit, integer)
+    endnewtype;
+
+    syntype maxit =Integer constants 0:25
+    endsyntype;
+  \end{lstlisting}
+
+  A blockchain can be regarded as a state machine~\cite{Duan2018} that contains a starting state, a non-empty state, the input transaction set,
+  a state transition function, and an acceptance state set. Which can be formally defined as:
+    \begin{displaymath}
+      S~\equiv(Q,\Sigma,\delta,s,F)
+    \end{displaymath}
+
+  Where:
+
+  \begin{enumerate}
+    \item[$\blacksquare$] Q is the non-empty state set, which represents all the states.
+    \item[$\blacksquare$] $\Sigma$ is the set of the newly generated and consensus blocks. 
+    \item[$\blacksquare$] $\delta$ represents the state transition function,
+      \begin{math}
+        \delta: Q \times \Sigma \rightarrow Q
+      \end{math}.
+    \item[$\blacksquare$] s would be the starting state, which is the state of the system when it initializes.
+      \begin{math}
+        \delta: s \in Q
+      \end{math}.
+    \item[$\blacksquare$] F representes the acceptance state set.
+      \begin{math}
+        F \subseteq Q
+      \end{math}.
+  \end{enumerate}
+  \  \\ %fake break line
+  The state of the model at the first block generation is the starting state.
+  As transactions are made, the model a leader node to generate the block, which is transmitted to the other nodes on the blockchain network,
+  triggering its validation for consensus. 
+  A consensus block stores the hash of the previous one and adds it to the end of the blockchain and completes the transfer of the blockchain state.
+
+  \subsubsection{Diagrams}
+  With a modelling language like SDL, we can use diagrams to define blockchain structural entities, like the core system of the consensus layer
+  and blocks. Process flowcharts can model the flow of information and input validation, making a process like
+  node validations of blocks and its subprocess of synchronization and voting can clearly illustrated.
+
+\section{Consensus Rule}
+Blockchain system may choose to use consensus rules taken from popular protocols such as Bitcoin,
+but an alternative rule can be implemented, and also be formally modelled~\cite{Kawahara2020}.
+
+On a consensus rule, fault tolerances requirements are of utmost importance, including the collusion of nodes to alter a ledger.
+In~\cite{Kawahara2020}, the author discusses a way to describe these tolerances with a scalable verification.
 

### 2022-01-13 article/article.tex
faulty states section

@@
 On a consensus rule, fault tolerances requirements are of utmost importance, including the collusion of nodes to alter a ledger.
-In~\cite{Kawahara2020}, the author discusses a way to describe these tolerances with a scalable verification.
+In~\cite{Kawahara2020}, the author discusses a way to formally describe these tolerances with a scalable verification.
+
+Endorsement policies, the rule that define the criteria of agreement os transaction results between nodes, can be described
+as a threshold function as follows:
+
+\begin{displaymath}
+  T(m,\textrm{node}_1,... ,\textrm{node}_n), m \in \mathbb{N}
+\end{displaymath}
+\linebreak[1]
+
+Where $T(2,\textrm{node}_1,\textrm{node}_2,\textrm{node}_3)$ would be an endorsement policy
+that means "among the three nodes in the argument, at least two nodes must return the same execution result".
+With this, we can mathematically model faulty state verification.
+
+\subsection{Faulty states}
+Let $\mathbb{B}$ and $\mathbb{N}$ be sets of Boolean and natural numbers, respectively. The state of the \textit{i}-th node can be defined as:
+$s_i = (s_i.e,s_i.v)$, where for each transaction execution, $s_i.e \in \mathbb{B}$ is the  existence of the result,
+and $s_i.v \in \mathbb{B}$ is the value of the result (correct or wrong).
+
+Using the threshold function previously shown, $T(m,s_1,... ,s_n) = (T.e,T.v)$. With this, let
+
+\begin{displaymath}
+  H_ = \left(\sum_{i}^{n} I(s_i.e \wedge (s_i.v = b)) \geq m \right)
+\end{displaymath}
+
+Where:
+
+\begin{enumerate}
+  \item[$\blacksquare$] \textit{m} is a treshold
+  \item[$\blacksquare$] $b \in \mathbb{B}$
+  \item[$\blacksquare$] $I : \mathbb{B} \mapsto \{0,1\}$  is the indicator function
+\end{enumerate}
+\  \\ %fake break line
+
+With the expression above, the author of~\cite{Kawahara2020} infers:
+
+\begin{displaymath}
+  T.e = H_{true} \vee H_{false},  T.v = \neg{H_{false}}
+\end{displaymath}
+
+The  endorsement policy $EP = (EP.e,EP.v)$ can be formed with \textit{T}. When $EP.e = \textrm{true}$, the policy
+is considered accordingly followed and the involved ledger is updated with the value of $EP.v$.
 

### 2022-01-14 article/article.tex
finish main sections

@@
 \usepackage{listings}
+\usepackage{makecell}
+\usepackage{tabularx}
 
@@
 \affiliation{%
-  \institution{Polytechnic Institute of Setubal}
+  \institution{Instituto Politécnico de Setúbal}
   \streetaddress{Campus do IPS - Estefanilha, 2910-761}
@@
 
-//TODO FINISH
+Contrasting with normal testing, formal verification is performed during the design process, it ensure the design is correct and allows the verification
+of any situation, while regular testing cannot test for every possible input~\cite{Murray2019}.
 
-\section{Formal Modeling Application}
+This paper is organized as follows. Section \ref{formalModeling} introduces applications of formal modeling of blockchain technology.
+Section \ref{consensusRule} expands on the use of formal mathematical descriptions of a blockchain's consensus rule.
+Section \ref{smartContracts} explored how formal modeling can be used to verify and assure quality to smart contracts using Colored Petri Nets (CPN).
+Section \ref{security} elaborates on the security requirements of a blockchain system.
+Section \ref{conclusion} is a brief conclusion.
+
+\section{Formal Modeling Application}\label{formalModeling}
 Blockchain systems can be divided into five main layers~\cite{Duan2018}: Data layer, Consensus layer, Smart contract layer and Application layer. 
@@
   \begin{lstlisting}[frame=single,label={lst:block-code},
-    caption={Definition of a block's structure},captionpos=b]
+    caption={Definition of a block's structure},captionpos=b, basicstyle=\ttfamily]
     newtype blockchain struct
@@
   \subsubsection{Diagrams}
-  With a modelling language like SDL, we can use diagrams to define blockchain structural entities, like the core system of the consensus layer
+  With a modeling language like SDL, we can use diagrams to define blockchain structural entities, like the core system of the consensus layer
   and blocks. Process flowcharts can model the flow of information and input validation, making a process like
@@
 
-\section{Consensus Rule}
+\section{Consensus Rule}\label{consensusRule}
 Blockchain system may choose to use consensus rules taken from popular protocols such as Bitcoin,
@@
 
-\subsection{Faulty states}
+\subsection{Faulty States}
 Let $\mathbb{B}$ and $\mathbb{N}$ be sets of Boolean and natural numbers, respectively. The state of the \textit{i}-th node can be defined as:
@@
 \begin{enumerate}
-  \item[$\blacksquare$] \textit{m} is a treshold
+  \item[$\blacksquare$] \textit{m} is a threshold
   \item[$\blacksquare$] $b \in \mathbb{B}$
@@
 \begin{displaymath}
-  T.e = H_{true} \vee H_{false},  T.v = \neg{H_{false}}
+  T.e = H_{\textrm{true}} \vee H_{\textrm{false}}, \quad T.v = \neg{H_{\textrm{false}}}
 \end{displaymath}
+\linebreak[1]
 
@@
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-    template parameters}.
+Mathematical descriptions like the ones above can also be applied to the fault tolerance of organizations participating in the blockchain in question.
+With formal modeling, a consensus rule can be tested and benchmarked after giving the test case some arbitrary requirements that are in conformity with the scope.
+The test results are used to judge the viability and scalability of the rule.
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
+\section{Smart Contracts}\label{smartContracts}
+Smart contracts are the backend code of decentralized applications that live in blockchains such as Ethereum. 
+This code cannot be changed once it is deployed to a production Net, so quality must be assured in order to guarantee
+that specifications are followed and that vulnerabilities are inexistent~\cite{Murray2019}.
+With the logic and mathematical modeling of formal verification, we avoid edge test cases that involve unforeseen inputs or conditions.
 
-\subsection{Template Styles}
+A smart contract's execution after its required verifications originates a transfer on a blockchain. Ethereum is a blockchain system
+that allows is to deploy decentralized applications based on smart contracts, which are written in Solidity~\cite{Murray2019}.
+Solidity has a limitation that makes smart contracts have a no parameters, no return value \textit{function()} that is anonymous
+and defined as the fallback function~\cite{Liu2019}. When a contract sends Ether (the Ethereum blockchain token) but does not
+not call any function, the fallback function is called. If this function does not exist int he contract, the transaction is cancelled.
+This limitation can be used by hackers to exploit the contract, like the DAO smart contract exploit in 2016~\cite{Liu2019}.
 
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
+A formal verification method using CPN modeling is proposed in~\cite{Liu2019}.
+In a scenario where a crowd funding smart contract (CFD) is considered, \cite{Liu2019} proposes a two layers contract modeling,
+the CFD layer model that establishes the overall structure of the contract, and a bottom layer that contains the AddTo layer
+and the WithDraw layer, which implement deposit and withdrawing functions.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{cfd-layer}
+  \caption{CFD Layer, from \cite{Liu2019}}
+  \Description{Ilustration of the layers that describe a blockchain system}
+  \label{fig:cfd-layer}
+\end{figure}
 
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-  \item {\verb|acmsmall|}: The default journal template style.
-  \item {\verb|acmlarge|}: Used by JOCCH and TAP.
-  \item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
+The CFD layer, shown on Figure~\ref{fig:cfd-layer}, presents the entity Account, that represents the user, Bank that represent
+the contract account, and Withdraw and AddTo, that represent withdrawing and depositing operations.
 
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-  \item {\verb|acmconf|}: The default proceedings template style.
-        \item{\verb|sigchi|}: Used for SIGCHI conference articles.
-        \item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-        \item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{add-to-layer}
+  \caption{AddTo Layer, from \cite{Liu2019}}
+  \Description{Ilustration of the layers that describe a blockchain system}
+  \label{fig:add-to-layer}
+\end{figure}
 
-\subsection{Template Parameters}
+The AddTo layer, shown on Figure~\ref{fig:add-to-layer}, models the user's depositing operations, where there are 
+3 transactions and 8 entities in the model that describe the steps of a given transaction in the blockchain and it's conditions.
 
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
+A similar to the on seen on Figure~\ref{fig:add-to-layer} was also presented in~\cite{Liu2019} for the WithDraw layer to describe the inherent processes
+of withdraw operations and all their conditions.
 
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-  \item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-        conference submission. Anonymizes the work and includes line
-        numbers. Use with the \verb|\acmSubmissionID| command to print the
-        submission's unique ID on each page of the work.
-        \item{\verb|authorversion|}: Produces a version of the work suitable
-        for posting by the author.
-        \item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
+Models like the proposed CPN model can be tested for resilience against malicious behavior using another model that attempts to exploit
+the CFD contract. We can plan our attack model to test any operation and condition, such as balance altering, assurance of reception of funds,
+etc. Smart contract's vulnerabilities can be taken advantage of by regular users executing expected operations, not only by badly intended actors 
+with knowledge in computer science,~so it makes sense that scenarios of no attack can also be part of the model checking. 
+CPN tools like Space State Tools can used to see the status of each step of a contract's execution during a test scenario~\cite{Liu2019},
+easing the discovert of vulnerabilities.
 
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigconf]{acmart}
-\end{verbatim}
+\section{Security}\label{security}
+As mentioned in section~\ref{formalModeling}, formal analysis and verification is used to assure security of a blockchain's core structures and consensus rule.
+But we can cover the security-requirements for backend blockchain protocol and mechanisms to ensure the assumptions and scripting language~\cite{Matsuo2017}.
 
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-  {\bfseries Your document will be returned to you for revision if
-    modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-  {\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-  \item the ``ACM Reference Format'' text on the first page.
-  \item the ``rights management'' text on the first page.
-  \item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
+In~\cite{Matsuo2017}, the authors enumerate security requirements of a blockchain system by their layers, consisting of cryptography layer, backbone protocol, application protocol,
+application logic, implementation and operation. These requirements can be seen in Table~\ref{tab:security-layers}.
 
   \begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
+    \caption{Blockchain Technology layers and security considerations}
+    \label{tab:security-layers}
+    \begin{tabularx}{\linewidth}{ccl}
       \toprule
-    Non-English or Math & Frequency   & Comments          \\
+      Layer&Security Consideration& Standard \\
+      \toprule
+      Operation & \makecell{Key Management, \\Audit, Backup} & ISO/IEC 27000 \\ 
       \midrule
-    \O                  & 1 in 1,000  & For Swedish names \\
-    $\pi$               & 1 in 5      & Common in math    \\
-    \$                  & 4 in 5      & Used in business  \\
-    $\Psi^2_1$          & 1 in 40,000 & Unexplained usage \\
+      Implementation & \makecell{Program Code,\\Secure Hardware} & ISO/IEC 15408 \\ 
+      \midrule
+      Application Logic & \makecell{Scripting Language\\for Financial\\Transaction,\\ Contract} & \makecell{Secure coding\\guides} \\ 
+      \midrule
+      Application Protocol & \makecell{Privacy protection,\\Secure transaction} & ISO/IEC 29128 \\ 
+      \midrule
+      Backbone Protocol & \makecell{PSP, Consensus,\\Merkle Tree} & ISO/IEC 29128 \\ 
+      \midrule
+      Cryptography & \makecell{ECDSA, SHA-2,\\RIPEMD160} & NIST, ISO \\
       \bottomrule
-  \end{tabular}
+  \end{tabularx}
   \end{table}
 
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command                    & A Number & Comments         \\
-    \midrule
-    \texttt{{\char'134}author} & 100      & Author           \\
-    \texttt{{\char'134}table}  & 300      & For tables       \\
-    \texttt{{\char'134}table*} & 400      & For wider tables \\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-    should not repeat the figure caption – their purpose is to capture
-    important information that is not already provided in the caption or
-    the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-Some examples.  A paginated journal article \cite{Afzaal2021}, an
-enumerated journal article \cite{Murray2019}, a reference to an entire
-issue \cite{Matsuo2017}, a monograph (whole book) \cite{Duan2018}, a
-monograph/whole book in a series (see 2a in spec. document)
-\cite{Kawahara2020}, a divisible-book such as an anthology or compilation
-\cite{Liu2019} followed by the same example, however we only output
-the series if the volume number is given.
+We can implement formal methods in the layers Implementation, Backbone protocol, Application protocol and Language for Smart Contract.
+In the implementation layer we have both software and hardware implementation pf security mechanisms, including the cryptographic algorithm,
+protocols and key management mechanisms. In the Backbone protocol and application protocol deals with cryptographic protocols.
+The security of the source code of a smart contracts are also mention in~\cite{Matsuo2017}, which can be modeled and verified according to requirements,
+as shown in section~\ref{smartContracts}.
 
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
-
 \end{document}

### 2022-01-14 article/article.tex
finished article

@@
 \begin{abstract}
-  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
-  Vestibulum enim nibh, aliquet sit amet ex suscipit, efficitur fringilla enim. 
-  Vestibulum elementum fringilla sodales. Cras malesuada sollicitudin consectetur.
-  Cras elit nibh, tempus elementum dui vitae, sagittis porttitor elit. In sollicitudin purus neque, eu tristique felis varius in. Morbi sed commodo eros.
-  Pellentesque ornare sed felis et bibendum.
+  Blockchain is a technology that allows the decentralized record keeping and monetary transactions.
+  Its different uses are constantly being explored and new projects emerge on a daily basis.
+  The underlying design of such systems can bring about dire consequences if deployed with an unclear design
+  and possible vulnerabilities. If we use formal methods to mathematically model the base structures of out blockchain
+  system we provide irrefutable proof that our design will work as intended. This includes the usage of modeling languages
+  to describe our system and block, mathematical descriptions of the applied consensus rule and endorsement policy and its different
+  security requirements, including a smart contract that contains the code of an application hosted in a blockchain.
+
 \end{abstract}
@@
 Knowing that the protocol of a given blockchain project is what dictates how transactions and their coordination is maintained, the assurance of security and safety is a given. 
-Formal methods can be introduced in order to provide unequivocal evidence that a given blockchain system and its consensus algorithm are secure and in according to expected software quality.
+Formal methods can be introduced in order to provide unequivocal evidence that a given blockchain system and its consensus algorithm and inherent smart contracts are secure and in according to expected software quality.
 
@@
 
-This paper is organized as follows. Section \ref{formalModeling} introduces applications of formal modeling of blockchain technology.
-Section \ref{consensusRule} expands on the use of formal mathematical descriptions of a blockchain's consensus rule.
-Section \ref{smartContracts} explored how formal modeling can be used to verify and assure quality to smart contracts using Colored Petri Nets (CPN).
-Section \ref{security} elaborates on the security requirements of a blockchain system.
-Section \ref{conclusion} is a brief conclusion.
+This paper is organized as follows. Section~\ref{formalModeling} introduces applications of formal modeling of blockchain technology.
+Section~\ref{consensusRule} expands on the use of formal mathematical descriptions of a blockchain's consensus rule.
+Section~\ref{smartContracts} explored how formal modeling can be used to verify and assure quality to smart contracts using Colored Petri Nets (CPN).
+Section~\ref{security} elaborates on the security requirements of a blockchain system.
+Section~\ref{conclusions} is a brief conclusion.
 
@@
   \begin{lstlisting}[frame=single,label={lst:block-code},
-    caption={Definition of a block's structure},captionpos=b, basicstyle=\ttfamily]
+    caption={Definition of a block's structure},captionpos=b, basicstyle=\ttfamily\small]
     newtype blockchain struct
@@
 
+  An example of a diagram that describes the system and a block can be seen on Figure~\ref{fig:system-block}.
+
+  \begin{figure}[h]
+    \centering
+    \includegraphics[width=\linewidth]{system-block-diagram}
+    \caption{System and block structure diagram, from~\cite{Duan2018}}
+    \Description{Ilustration of the layers that describe a blockchain system}
+    \label{fig:system-block}
+  \end{figure}
+
 \section{Consensus Rule}\label{consensusRule}
@@
 \begin{displaymath}
-  H_ = \left(\sum_{i}^{n} I(s_i.e \wedge (s_i.v = b)) \geq m \right)
+  H_b = \left(\sum_{i}^{n} I(s_i.e \wedge (s_i.v = b)) \geq m \right)
 \end{displaymath}
@@
       \toprule
-      Operation & \makecell{Key Management, \\Audit, Backup} & ISO/IEC 27000 \\ 
+      Operation & \makecell{Key Management,\\Audit, Backup} & ISO/IEC 27000 \\ 
       \midrule
@@
 
+\section{Conclusions}\label{conclusions}
+If we apply formal methods to Blockchain technology and its inherent structures and properties we can have a clear vision of the implementation
+of its design.
+
+The nodes of a blockchain system can be mathematically described in a way that we can predict its behavior.
+The same can be done for the state of the blockchain at a given moment. The same mathematical predictability
+can be applied to the description of endorsement policies. Smart contracts also benefit from formal verification,
+since their code can be an application used by common users, and CPN with tools like Space State Tools can provide
+a way of formally verifying the design of a contract.
+A blockchain system that was planned using formal methods benefit from assured security in the requirement layers
+that were considered.
+
 %%
